---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE,
  warning = FALSE,
  fig.retina = 2,
  fig.align = 'center'
)

library(tidyverse)
library(epoxy)
library(washinvestments)
```

# washinvestments

<!-- badges: start -->
<!-- badges: end -->

The goal of washinvestments is to ...

## Installation

You can install the development version of washinvestments from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("openwashdata/washinvestments")
```

## Project goal

TODO

## Data

TODO

The package provides access to one data set.

```{r, echo = TRUE}
library(washinvestments)
```

The `washinvestments` data set has `r ncol(washinvestments)`
variables and `r nrow(washinvestments)` observations. For an overview
of the variable names, see the following table.

```{r, eval=FALSE}
washinvestments
```

```{r, echo=FALSE}
readr::read_csv("data-raw/dictionary.csv") |> 
  dplyr::filter(file_name == "washinvestments.rda") |> 
  dplyr::select(variable_name:description) |> 
  knitr::kable()
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(washinvestments)
## basic example code
```

## License

Data are available as 
[CC-BY](https://github.com/openwashdata/washinvestments/LICENSE.md).

## Citation

To cite this package, please use:

```{r}
citation("washinvestments")
```
