---
output: github_document
always_allow_html: true
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: console
bibliography: references.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE,
  warning = FALSE,
  fig.retina = 2,
  fig.align = 'center'
)

library(tidyverse)
library(epoxy)
library(washinvestments)
```

# washinvestments

<!-- badges: start -->
<!-- badges: end -->

The goal of washinvestments is to provide users documentation on the newly created data set published alongside the article "Multilateral development banks investment behaviour in water and sanitation: Findings and lessons from 60 years of investment projects in Africa and Asia" [@heidler2023multilateral]. This data set was compiled by drawing on 3,639 water and sanitation projects and assess territorial trends, technology choices, distribution of financial burdens, and reforms to institutional arrangements to assess the investment behaviour of the World Bank, ADB, and AfDB in water supply and sanitation from their first operations in the 1960s until 2020 and distil how they responded to trends in urbanization and the policy debates about governing access to basic services.

## Installation

You can install the development version of washinvestments from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("openwashdata/washinvestments")
```

Alternatively, you can download the dataset as a CSV or XLSX
file from the table below.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

extdata_path <- "https://github.com/openwashdata/washinvestments/raw/main/inst/extdata/"

read_csv("data-raw/dictionary.csv") |> 
  distinct(file_name) |> 
  dplyr::mutate(file_name = str_remove(file_name, ".rda")) |> 
  dplyr::rename(dataset = file_name) |> 
  mutate(
    CSV = paste0("[Download CSV](", extdata_path, dataset, ".csv)"),
    XLSX = paste0("[Download XLSX](", extdata_path, dataset, ".xlsx)")
  ) |> 
  knitr::kable()

```

## Project goal

'Multilateral development banks (MDBs) play a pivotal role in financing water and sanitation infrastructure projects and thus have a major
impact on the development of basic services. Although information about the MDBs’ investments is publicly available, it is dispersed and
not easily comparable. A comprehensive compilation of MDBs’ water and sanitation investments has long been lacking. To address this
gap, we assess water and sanitation financing by the three MDBs most relevant to Africa and Asia between 1960 and 2020: the World
Bank, the African Development Bank, and the Asian Development Bank. We compile a new dataset by drawing on 3,639 water and sanitation
projects and assess territorial trends, technology choices, distribution of financial burdens, and reforms to institutional arrangements. We
find that MDBs’ investments align with changing patterns of urbanization and increasingly finance sanitation infrastructures including
non-sewered technologies. However, our results also suggest that institutional reforms have addressed utility efficiency through investment
in equipment and skills rather than through increased commercialization and private sector participation. The leverage effect of MDB investment on private financing is negligible, whereas co-financing from local governments dominates' [@heidler2023multilateral].

## Data

The data set includes information about water and sanitation projects conducted in Africa and Asia between 1960 and 2020.

![]()

The package provides access to one data set.

```{r, echo = TRUE}
library(washinvestments)
```

The `washinvestments` data set has `r ncol(washinvestments)`
variables and `r nrow(washinvestments)` observations. For an overview
of the variable names, see the following table.

```{r, eval=FALSE}
washinvestments
```

```{r, echo=FALSE}
readr::read_csv("data-raw/dictionary.csv") |> 
  dplyr::filter(file_name == "washinvestments.rda") |> 
  dplyr::select(variable_name:description) |> 
  knitr::kable()
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(washinvestments)

```

## License

Data are available as 
[CC-BY](https://github.com/openwashdata/washinvestments/LICENSE.md).

## Citation

To cite this package, please use:

```{r}
citation("washinvestments")
```
